---
title: "QC report"
output: html_document
params:
  input_abundance: 
  input_id: 
  input_exp_design: 
  input_internal_standards: 
  id_name:
  id_mz: 
  id_rt: 
  id_check_rt: 
  id_convert_rt_to_seconds: 
  id_use_rt: 
  color_by:
  interactive:
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(ggplot2)
library(plotly)
knitr::opts_chunk$set(echo = TRUE)
```

```{r,echo=FALSE}
data_abundance <- read.table(file = params$input_abundance,header = TRUE,sep = "\t",comment.char = "",stringsAsFactors = FALSE)
colnames(data_abundance) <- gsub("\\.mzML$",replacement = "",colnames(data_abundance))
data_abundance[is.na(data_abundance)]<-NA

data_exp_design <- read.table(file = params$input_exp_design,header = TRUE,sep = "\t",comment.char = "",stringsAsFactors = FALSE)
if(!is.null(params$input_internal_standards))
internal_standards <- read.table(file = params$input_internal_standards,header = TRUE,sep = "\t",comment.char = "",stringsAsFactors = FALSE)

if(!is.null(params$input_id))
data_identification <- read.table(file = params$input_id,header = TRUE,sep = "\t",comment.char = "",stringsAsFactors = FALSE)


print_qc_standards <- !is.null(params$input_internal_standards) & nrow(internal_standards)>1 & !is.null(params$input_id)

if(!all(c("file_name","runorder")%in%colnames(data_exp_design)))
  stop("The experimental design file must at least contain file_name and runorder!")

if(!params$color_by%in%colnames(internal_standards))
{
 
  color_by<-NULL
}else{
  color_by=params$color_by
}

  
  
data_exp_design <- data_exp_design[order(data_exp_design[,"runorder"]),]

column_names_cmp <- lapply(c("rt","intensity","charge","width","mz"),function(x){paste(x,data_exp_design[,"file_name"],sep="_")})
names(column_names_cmp)<-c("rt","intensity","charge","width","mz")

if(!all(sapply(column_names_cmp,function(x){all(x%in%colnames(data_abundance))})))
{
  incor_names<-gsub(pattern = "^rt_|^intensity_|^charge_|^width_|^mz_",
       unlist(sapply(column_names_cmp,function(x){x[!x%in%colnames(data_abundance)]})),replacement = "")
  stop("The file names in the experimental design file must match the raw data (this is case sensitive)! The names must not contain the file extension!"," check:", paste(unique(incor_names),collapse =" "))
}




if(length(column_names_cmp)>10){
  show_text<-element_text(angle = 90)
}else{
   show_text=element_blank()
}
```


## Global QC

### Missing values

Percentage of missing values compared to the total number of features find in the *entire* dataset
```{r, echo=FALSE,warning=FALSE,error=FALSE,message=FALSE}

missing_data<-apply(is.na(data_abundance[,column_names_cmp[["intensity"]]]),
      2,sum)/nrow(data_abundance)
missing_data<-missing_data*100
plot_missing_data<-data.frame(data_exp_design,missing_data=missing_data)

plot_missing_data[,"file_name"]<-factor(plot_missing_data[,"file_name"],levels = plot_missing_data[,"file_name"])

if(params$interactive)
{
  plotly::ggplotly(ggplot(data = plot_missing_data,aes_string(x="file_name",y="missing_data",color=color_by))+geom_point()+
  geom_smooth(aes_string(x="runorder",y="missing_data",color=NULL),alpha=0.3) +theme_classic()+xlab("")+ylab("Missing value percentage")+theme(axis.text.x = show_text)+ylim(0,100))

}else{
 (ggplot(data = plot_missing_data,aes_string(x="file_name",y="missing_data",color=color_by))+geom_point()+
  geom_smooth(aes_string(x="runorder",y="missing_data",color=NULL),alpha=0.3) +theme_classic()+xlab("")+ylab("Missing value percentage")+theme(axis.text.x = show_text)+ylim(0,100))
}


```

### TIC across the run order

This plots shows the $log_2$ of TIC over the runorder

```{r, echo=FALSE,warning=FALSE,error=FALSE,message=FALSE}

tic_data<-apply((data_abundance[,column_names_cmp[["intensity"]]]),
      2,sum,na.rm=TRUE)
tic_data<-log2(missing_data)
plot_missing_data<-data.frame(data_exp_design,tic_data=tic_data)

plot_missing_data[,"file_name"]<-factor(plot_missing_data[,"file_name"],levels = plot_missing_data[,"file_name"])
if(params$interactive)
{
plotly::ggplotly(ggplot(data = plot_missing_data,aes_string(x="file_name",y="tic_data",color=color_by))+geom_point()+
  geom_smooth(aes_string(x="runorder",y="tic_data",color=NULL),alpha=0.3) +theme_classic()+xlab("")+ylab("Log2 of TIC")+theme(axis.text.x = show_text))
}else{
  ggplot(data = plot_missing_data,aes_string(x="file_name",y="tic_data",color=color_by))+geom_point()+
  geom_smooth(aes_string(x="runorder",y="tic_data",color=NULL),alpha=0.3) +theme_classic()+xlab("")+ylab("Log2 of TIC")+theme(axis.text.x = show_text)
}
```

### CV across the run order

This plots shows the CV over the runorder. The dashed line shows the median of CV.

```{r, echo=FALSE,warning=FALSE,error=FALSE,message=FALSE}

   CV<-function(x)
        {
		if(length(na.omit(x))<=2)return(NA)
          sd(x,na.rm = T)/mean(x,na.rm = T)
   }

hist_data<-data.frame(x=apply((data_abundance[,column_names_cmp[["intensity"]]]),
      1,CV))

if(params$interactive)
{
plotly::ggplotly(ggplot(data = hist_data,aes_string(x="x"))+geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="blue")+
   geom_vline(aes(xintercept=median(hist_data$x,na.rm = T)),
            color="blue", linetype="dashed", size=1) +theme_classic()+xlab("CV"))
}else{
  ggplot(data = hist_data,aes_string(x="x"))+geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="blue")+
   geom_vline(aes(xintercept=median(hist_data$x,na.rm = T)),
            color="blue", linetype="dashed", size=1) +theme_classic()+xlab("CV")
}
```


### mz and retention time deviance

#### RT
This plots retention time deviation compared to the median retention time for each feature

```{r, echo=FALSE,warning=FALSE,error=FALSE,message=FALSE}



rt_median<-apply((data_abundance[,column_names_cmp[["rt"]]]),
      1,median,na.rm=TRUE)




rt_dev<-sweep(as.matrix(data_abundance[,column_names_cmp[["rt"]]]), 1, rt_median)

dt_fr<-data.frame(data_abundance[,column_names_cmp[["rt"]]],dev=rt_dev[,2])

dt_fr<-reshape2::melt(dt_fr,measure.vars=c(column_names_cmp[["rt"]]))

colnames(dt_fr)[colnames(dt_fr)=="variable"]<-"file_name"
levels(dt_fr[,"file_name"])<-gsub("^rt_",replacement = "",levels(dt_fr[,"file_name"]))
dt_fr<-merge.data.frame(dt_fr,data_exp_design,by="file_name")


if(params$interactive)
{
plotly::ggplotly(ggplot(data = dt_fr,aes_string(x="value",y="dev",color=color_by))+geom_point()+
  geom_smooth(aes_string(x="value",y="dev",group="file_name"),alpha=0.3,se = FALSE)
  +theme_classic()+xlab("m/z")+ylab("Deviation"))
}else{
  ggplot(data = dt_fr,aes_string(x="value",y="dev",color=color_by))+geom_point()+
  geom_smooth(aes_string(x="value",y="dev",group="file_name"),alpha=0.3,se = FALSE)+theme_classic()+xlab("m/z")+ylab("Deviation")
}

```

This is showing the distribution of RT deviation


```{r, echo=FALSE,warning=FALSE,error=FALSE,message=FALSE}



rt_median<-apply((data_abundance[,column_names_cmp[["rt"]]]),
      1,median,na.rm=TRUE)

rt_dev<-sweep(as.matrix(data_abundance[,column_names_cmp[["rt"]]]), 1, rt_median)

rt_hist<-data.frame(x=as.vector(rt_dev))
if(params$interactive)
{
plotly::ggplotly(ggplot(data = rt_hist,aes_string(x="x"))+geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="blue") +theme_classic()+xlab("RT"))
}else{
  ggplot(data = rt_hist,aes_string(x="x"))+geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="blue") +theme_classic()+xlab("RT")
}
```

#### mz


```{r, echo=FALSE,warning=FALSE,error=FALSE,message=FALSE}



mz_median<-apply((data_abundance[,column_names_cmp[["mz"]]]),
      1,median,na.rm=TRUE)

mz_dev<-sweep(as.matrix(data_abundance[,column_names_cmp[["mz"]]]), 1, mz_median)
mz_dev<-sweep(mz_dev, MARGIN = 1,FUN = "/", mz_median)*1000000
  

dt_fr<-data.frame(data_abundance[,column_names_cmp[["mz"]]],dev=mz_dev[,2])

dt_fr<-reshape2::melt(dt_fr,measure.vars=c(column_names_cmp[["mz"]]))

colnames(dt_fr)[colnames(dt_fr)=="variable"]<-"file_name"
levels(dt_fr[,"file_name"])<-gsub("^mz_",replacement = "",levels(dt_fr[,"file_name"]))
dt_fr<-merge.data.frame(dt_fr,data_exp_design,by="file_name")

if(params$interactive)
{
plotly::ggplotly(ggplot(data = dt_fr,aes_string(x="value",y="dev",color=color_by))+geom_point()+
  geom_smooth(aes_string(x="value",y="dev",group="file_name"),alpha=0.3,se = FALSE)
  +theme_classic()+xlab("m/z")+ylab("Deviation (ppm)"))
}else{
  ggplot(data = dt_fr,aes_string(x="value",y="dev",color=color_by))+geom_point()+
  geom_smooth(aes_string(x="value",y="dev",group="file_name"),alpha=0.3,se = FALSE)+theme_classic()+xlab("m/z")+ylab("Deviation (ppm)")
}

```

This is showing the distribution of m/z deviation (ppm)


```{r, echo=FALSE,warning=FALSE,error=FALSE,message=FALSE}


mz_hist<-data.frame(x=as.vector(mz_dev))
if(params$interactive)
{
plotly::ggplotly(ggplot(data = mz_hist,aes_string(x="x"))+geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="blue") +theme_classic()+xlab("Deviation (ppm)"))
}else{
  ggplot(data = mz_hist,aes_string(x="x"))+geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="blue") +theme_classic()+xlab("Deviation (ppm)")
}
```


### Charge state across different runs

```{r, echo=FALSE,warning=FALSE,error=FALSE,message=FALSE}

#charge_data<-apply(data_abundance[,column_names_cmp[["charge"]]],2,function(x){(table(x)/length(x))*100})
 charge_data<-lapply(split(t(data_abundance[,column_names_cmp[["charge"]]]),seq(NROW(t(data_abundance[,column_names_cmp[["charge"]]])))),
                     function(x){(table(as.numeric(x))/length(x))*100})
names(charge_data)<-colnames(data_abundance[,column_names_cmp[["charge"]]])
all_charges<-sort(unique(as.vector(unlist(sapply(charge_data,names)))))
all_charges_U<-sort(unique(as.vector(unlist(sapply(charge_data,names)))))
all_charges<-data.frame(sample=column_names_cmp[["charge"]],
                        charge=rep(all_charges,each=length(column_names_cmp[["charge"]])),count_qc=NA,
                        do.call(rbind, replicate(length(all_charges), data_exp_design, simplify=FALSE)))




for(x in names(charge_data))
{
  fk_dt<-rep(NA,length(all_charges_U))
  names(fk_dt)<-all_charges_U
  fk_dt[names(charge_data[[x]])]<-charge_data[[x]]
  all_charges[all_charges$sample==x,"count_qc"]<-fk_dt
}


all_charges$sample<-factor(all_charges$sample,levels = column_names_cmp[["charge"]])

levels(all_charges$sample)<-gsub("charge_",all_charges$sample,replacement = "")

if(params$interactive)
{
plotly::ggplotly(ggplot(data=all_charges, aes_string(x="sample", y="count_qc",color=color_by)) +  geom_point()+
     geom_smooth(aes_string(x="sample",y="count_qc",group="charge"),se = FALSE)+
facet_wrap(~charge,scales = "free")+
  theme_classic()+xlab("")+ylab("Percentage of charge")+theme(axis.text.x = show_text))
}else{
  
  ggplot(data=all_charges, aes_string(x="sample", y="count_qc",color=color_by)) +  geom_point()+
     geom_smooth(aes_string(x="sample",y="count_qc",group="charge"),se = FALSE)+
facet_wrap(~charge,scales = "free")+
  theme_classic()+xlab("")+ylab("Percentage of charge")+theme(axis.text.x = show_text)
}

```

### Consistent charge

This plot shows the percentage of features that have consistent charge state across the runs

```{r, echo=FALSE,warning=FALSE,error=FALSE,message=FALSE}


charge_data<-lapply(split((data_abundance[,column_names_cmp[["charge"]]]),seq(NROW((data_abundance[,column_names_cmp[["charge"]]])))),
                     function(x){(table(as.numeric(x))/length(x))*100})

all_charges<-reshape2::melt(table(unlist(sapply(charge_data,function(x){names(x[x==100])})))*100/nrow(data_abundance))

if(params$interactive)
{
plotly::ggplotly(ggplot(data=all_charges, aes(x="charge", y=value,fill=as.character(Var1))) +  geom_bar(stat = "identity",position="stack")+
  theme_classic()+xlab("")+ylab("Percentage of charge")+theme(legend.title=element_blank())+ylim(0,100))
}else{
  ggplot(data=all_charges, aes(x="charge", y=value,fill=as.character(Var1))) +  geom_bar(stat = "identity",position="stack")+
  theme_classic()+xlab("")+ylab("Percentage of charge")+theme(legend.title=element_blank())+ylim(0,100)
}



```


```{r, echo=FALSE,warning=FALSE,error=FALSE,message=FALSE,include=print_qc_standards,eval=print_qc_standards}

 knitr::asis_output("
 
 ## Internal standard-based QC
 
                    ")

 knitr::asis_output("
 
 ### Identification
                    ")
                    
# what has been identified!
unique_ids_database<-NA
unique_ids_exp <- NA
if(params$id_use_rt)
{
  unique_ids_database<-unique(apply(internal_standards[,c(params$id_mz,params$id_rt)],1,function(x){paste(x,collapse = "_")}))
  unique_ids_exp<-unique(apply(data_identification[,c("mz",params$id_rt)],1,function(x){paste(x,collapse = "_")}))
  ids_exp<-apply(data_identification[,c("mz",params$id_rt)],1,function(x){paste(x,collapse = "_")})
}else{
  
    unique_ids_database<-unique(as.character(internal_standards[,c(params$id_mz)]))
  unique_ids_exp<-unique(as.character(data_identification[,"mz"]))
    ids_exp<-as.character(data_identification[,"mz"])

}

 knitr::asis_output( paste( "\nThe total number of identified metabolites is ",length(intersect(unique_ids_database,unique_ids_exp)), " out of ",length(unique_ids_database),". In addition, ",length(unique(data_identification[duplicated(data_identification[,"Met_ID"]),"Met_ID"]))," metabolites were not assigned to a unique feature.
Finally, ", length(unique(ids_exp[duplicated(ids_exp)]))," metabolites were assigned to multiple features.\n")) 
 

knitr::asis_output("

### QC based on Identification
")

## limit the data to the identified one!

data_abundance<-data_abundance[data_abundance[,"Met_ID"]%in%data_identification[,"Met_ID"],,drop=FALSE]

knitr::asis_output("
### Missing values
                   ")
knitr::asis_output("

Percentage of missing values compared to the total number of features find in the *entire* dataset
                   
                   ")

missing_data<-apply(is.na(data_abundance[,column_names_cmp[["intensity"]]]),
      2,sum)/nrow(data_abundance)
missing_data<-missing_data*100
plot_missing_data<-data.frame(data_exp_design,missing_data=missing_data)

plot_missing_data[,"file_name"]<-factor(plot_missing_data[,"file_name"],levels = plot_missing_data[,"file_name"])
if(params$interactive)
{
plotly::ggplotly(ggplot(data = plot_missing_data,aes_string(x="file_name",y="missing_data",color=color_by))+geom_point()+
  geom_smooth(aes_string(x="runorder",y="missing_data",color=NULL),alpha=0.3) +theme_classic()+xlab("")+ylab("Missing value percentage")+theme(axis.text.x = show_text)+ylim(0,100))
}else{
print(  ggplot(data = plot_missing_data,aes_string(x="file_name",y="missing_data",color=color_by))+geom_point()+
  geom_smooth(aes_string(x="runorder",y="missing_data",color=NULL),alpha=0.3) +theme_classic()+xlab("")+ylab("Missing value percentage")+theme(axis.text.x = show_text)+ylim(0,100))
}
###
knitr::asis_output(
"### TIC across the run order
")

knitr::asis_output("
This plots shows the $log_2$ of TIC over the runorder
                   ")

tic_data<-apply((data_abundance[,column_names_cmp[["intensity"]]]),
      2,sum,na.rm=TRUE)
tic_data<-log2(missing_data)
plot_missing_data<-data.frame(data_exp_design,tic_data=tic_data)

plot_missing_data[,"file_name"]<-factor(plot_missing_data[,"file_name"],levels = plot_missing_data[,"file_name"])
if(params$interactive)
{
plotly::ggplotly(ggplot(data = plot_missing_data,aes_string(x="file_name",y="tic_data",color=color_by))+geom_point()+
  geom_smooth(aes_string(x="runorder",y="tic_data",color=NULL),alpha=0.3) +theme_classic()+xlab("")+ylab("Log2 of TIC")+theme(axis.text.x = show_text))
}else{
  ggplot(data = plot_missing_data,aes_string(x="file_name",y="tic_data",color=color_by))+geom_point()+
  geom_smooth(aes_string(x="runorder",y="tic_data",color=NULL),alpha=0.3) +theme_classic()+xlab("")+ylab("Log2 of TIC")+theme(axis.text.x = show_text)
}
knitr::asis_output("
### CV across the run order

This plots shows the CV over the runorder. The dashed line shows the median of CV."
)


   CV<-function(x)
        {
		if(length(na.omit(x))<=2)return(NA)
          sd(x,na.rm = T)/mean(x,na.rm = T)
   }

hist_data<-data.frame(x=apply((data_abundance[,column_names_cmp[["intensity"]]]),
      1,CV))

if(params$interactive)
{
plotly::ggplotly(ggplot(data = hist_data,aes_string(x="x"))+geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="blue")+
   geom_vline(aes(xintercept=median(hist_data$x,na.rm = T)),
            color="blue", linetype="dashed", size=1) +theme_classic()+xlab("CV"))
}else{
  ggplot(data = hist_data,aes_string(x="x"))+geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="blue")+
   geom_vline(aes(xintercept=median(hist_data$x,na.rm = T)),
            color="blue", linetype="dashed", size=1) +theme_classic()+xlab("CV")
}
knitr::asis_output("
### CV individual standars

This plots shows the CV over the runorder for each ID"
)

for(i in 1:nrow(hist_data))
{
    data_points<-data_abundance[i,column_names_cmp[["intensity"]]]
    met_id<-data_abundance[i,"Met_ID"]
    metabo_names <- paste("ID: ",met_id, " Name(s): ",
                          paste(data_identification[data_identification[,"Met_ID"]==met_id,params$id_name],sep="/"),
                          "CV: ",hist_data[i,"x"])
plot_point_data<-data.frame(data_exp_design,points=log2(as.numeric(data_points)))

plot_point_data[,"file_name"]<-factor(plot_point_data[,"file_name"],levels = plot_point_data[,"file_name"])
if(params$interactive)
{
(plotly::ggplotly(ggplot(data = plot_point_data,aes_string(x="file_name",
                                                          y="points",color=color_by))+geom_point()+
  geom_smooth(aes_string(x="runorder",y="points",color=NULL),alpha=0.3) +theme_classic()+xlab("")+ylab("Log2 intensity")+
    theme(axis.text.x = show_text)+ggtitle(metabo_names)))
}else{
  ggplot(data = plot_point_data,aes_string(x="file_name",
                                                          y="points",color=color_by))+geom_point()+
  geom_smooth(aes_string(x="runorder",y="points",color=NULL),alpha=0.3) +theme_classic()+xlab("")+ylab("Log2 intensity")+
    theme(axis.text.x = show_text)+ggtitle(metabo_names)
}

}

knitr::asis_output("
### mz and retention time deviance

#### RT

This plots retention time deviation compared to the median retention time for each feature
"
)

rt_median<-apply((data_abundance[,column_names_cmp[["rt"]]]),
      1,median,na.rm=TRUE)

rt_dev<-sweep(as.matrix(data_abundance[,column_names_cmp[["rt"]]]), 1, rt_median)


dt_fr<-data.frame(data_abundance[,column_names_cmp[["rt"]]],dev=rt_dev[,2])

dt_fr<-reshape2::melt(dt_fr,measure.vars=c(column_names_cmp[["rt"]]))

colnames(dt_fr)[colnames(dt_fr)=="variable"]<-"file_name"
levels(dt_fr[,"file_name"])<-gsub("^rt_",replacement = "",levels(dt_fr[,"file_name"]))
dt_fr<-merge.data.frame(dt_fr,data_exp_design,by="file_name")


if(params$interactive)
{
plotly::ggplotly(ggplot(data = dt_fr,aes_string(x="value",y="dev",color=color_by))+geom_point()+
  geom_smooth(aes_string(x="value",y="dev",group="file_name"),alpha=0.3,se = FALSE)
  +theme_classic()+xlab("Retention time")+ylab("Deviation"))
}else{
  ggplot(data = dt_fr,aes_string(x="value",y="dev",color=color_by))+geom_point()+
  geom_smooth(aes_string(x="value",y="dev",group="file_name"),alpha=0.3,se = FALSE)+theme_classic()+xlab("Retention time")+ylab("Deviation")
}
knitr::asis_output("

This is showing the distribution of RT deviation
"
)

rt_median<-apply((data_abundance[,column_names_cmp[["rt"]]]),
      1,median,na.rm=TRUE)

rt_dev<-sweep(as.matrix(data_abundance[,column_names_cmp[["rt"]]]), 1, rt_median)

rt_hist<-data.frame(x=as.vector(rt_dev))
if(params$interactive)
{
plotly::ggplotly(ggplot(data = rt_hist,aes_string(x="x"))+geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="blue") +theme_classic()+xlab("RT"))
}else{
  ggplot(data = rt_hist,aes_string(x="x"))+geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="blue") +theme_classic()+xlab("RT")
  
}

knitr::asis_output("

#### mz

"
)


mz_median<-apply((data_abundance[,column_names_cmp[["mz"]]]),
      1,median,na.rm=TRUE)

mz_dev<-sweep(as.matrix(data_abundance[,column_names_cmp[["mz"]]]), 1, mz_median)
mz_dev<-sweep(mz_dev, MARGIN = 1,FUN = "/", mz_median)*1000000
  
dt_fr<-data.frame(data_abundance[,column_names_cmp[["mz"]]],dev=mz_dev[,2])

dt_fr<-reshape2::melt(dt_fr,measure.vars=c(column_names_cmp[["mz"]]))

colnames(dt_fr)[colnames(dt_fr)=="variable"]<-"file_name"
levels(dt_fr[,"file_name"])<-gsub("^mz_",replacement = "",levels(dt_fr[,"file_name"]))
dt_fr<-merge.data.frame(dt_fr,data_exp_design,by="file_name")

if(params$interactive)
{
plotly::ggplotly(ggplot(data = dt_fr,aes_string(x="value",y="dev",color=color_by))+geom_point()+
  geom_smooth(aes_string(x="value",y="dev",group="file_name"),alpha=0.3,se = FALSE)
  +theme_classic()+xlab("m/z")+ylab("Deviation"))
}else{
  
  ggplot(data = dt_fr,aes_string(x="value",y="dev",color=color_by))+geom_point()+
  geom_smooth(aes_string(x="value",y="dev",group="file_name"),alpha=0.3,se = FALSE)+theme_classic()+xlab("m/z")+ylab("ppm error")
}
knitr::asis_output("

This is showing the distribution of m/z deviation
"
)

mz_hist<-data.frame(x=as.vector(mz_dev))
if(params$interactive)
{
plotly::ggplotly(ggplot(data = mz_hist,aes_string(x="x"))+geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="blue") +theme_classic()+xlab("ppm error"))
}else{
  ggplot(data = mz_hist,aes_string(x="x"))+geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="blue") +theme_classic()+xlab("ppm error")
}

knitr::asis_output("
### mz deviation of individual metabolites

This is showing the distribution of m/z deviation (ppm) of each matched metabolite
"
)


for(i in 1:nrow(data_abundance))
{
  
  data_points<-data_abundance[i,column_names_cmp[["mz"]]]
  met_id<-data_abundance[i,"Met_ID"]
  id_tmp<-data_identification[data_identification[,"Met_ID"]==met_id,,drop=FALSE]
  con_mz<-data_abundance[i,"mz_cf"]
  for(j in 1:nrow(id_tmp))
  {
    theo_mass<-as.numeric(id_tmp[j,"mz"])
    data_points_def<-data_points-theo_mass
  data_points_def<-(data_points_def/theo_mass)*1000000
    
  con_dev<-((con_mz-theo_mass)/theo_mass)*1000000
  
  metabo_names <- paste("ID: ",met_id, " Name: ",
                          paste(id_tmp[j,params$id_name],sep="/"),
                          "Consensus mass dev ppm: ",con_dev)
  
  
  
  plot_point_data<-data.frame(data_exp_design,points=(as.numeric(data_points_def)))
  if(params$interactive)
{
  (plotly::ggplotly(ggplot(data = plot_point_data,aes_string(x="file_name",
                                                          y="points",color=color_by))+geom_point()+
  geom_smooth(aes_string(x="runorder",y="points",color=NULL),alpha=0.3) +theme_classic()+xlab("")+ylab("ppm error")+
    theme(axis.text.x = show_text)+ggtitle(metabo_names)))
  }else{
 print(  ggplot(data = plot_point_data,aes_string(x="file_name",
                                                          y="points",color=color_by))+geom_point()+
  geom_smooth(aes_string(x="runorder",y="points",color=NULL),alpha=0.3) +theme_classic()+xlab("")+ylab("ppm error")+
    theme(axis.text.x = show_text)+ggtitle(metabo_names))
  }
  
  }
}


if(params$id_check_rt==TRUE)
{
  
  knitr::asis_output("
### RT deviation of individual metabolites

This is showing the distribution of RT deviation of each matched metabolite
"
)

for(i in 1:nrow(data_abundance))
{
  
  data_points<-data_abundance[i,column_names_cmp[["rt"]]]
  met_id<-data_abundance[i,"Met_ID"]
  id_tmp<-data_identification[data_identification[,"Met_ID"]==met_id,,drop=FALSE]
  con_rt<-data_abundance[i,"rt_cf"]
  for(j in 1:nrow(id_tmp))
  {
    theo_rt<-as.numeric(id_tmp[j,params$id_rt])
    data_points_def<-data_points-theo_rt
  
  con_dev<-(con_rt-theo_rt)
  metabo_names <- paste("ID: ",met_id, " Name: ",
                          paste(id_tmp[j,params$id_name],sep="/"),
                          "Consensus mass dev ppm: ",con_dev)
  plot_point_data<-data.frame(data_exp_design,points=(as.numeric(data_points_def)))
    if(params$interactive)
{
  (plotly::ggplotly(ggplot(data = plot_point_data,aes_string(x="file_name",
                                                          y="points",color=color_by))+geom_point()+
  geom_smooth(aes_string(x="runorder",y="points",color=NULL),alpha=0.3) +theme_classic()+xlab("")+ylab("RT dev")+
    theme(axis.text.x = show_text)+ggtitle(metabo_names)))
    }else{
    print(  ggplot(data = plot_point_data,aes_string(x="file_name",
                                                          y="points",color=color_by))+geom_point()+
  geom_smooth(aes_string(x="runorder",y="points",color=NULL),alpha=0.3) +theme_classic()+xlab("")+ylab("RT dev")+
    theme(axis.text.x = show_text)+ggtitle(metabo_names))
    }
  
  }
}
}

```





